What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Folded in more changes from Barbara

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\

        570,000,000 & think that & 28\%& 69\%\\
        495,000,000 & believe that & 48\%& 65\%\\
        145,000,000 & idea that & 42\% & 61\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans think that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''. 
 \end{itemize}

@@

We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. In each case, we trained the classifier on the data set for the other patterns in the same group and then tested its performance on the result for that pattern.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawins2006} seems to have sparked extra controversy.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

>>>>

\begin{figure}[tb]
\begin{center}
  \begin{tabular}{|llll|}
    \hline
    {\bf Frequency$^*$} & {\bf Pattern} & {\bf Pattern} & {\bf Classifier}\\ 
    {\bf on the web} &                   & {\bf Precision} & {\bf Accuracy}\\
    \hline
        \multicolumn{2}{|l}{\it Plausible to not believe it} & &\\
	    & & &\\
        495,000,000 & believe that & 48\%& 65\%\\
        101,000,000 & claim that & 46\%& 72\%\\
       \hline
       \multicolumn{2}{|l}{\it It is notable that others believe it} & &\\
           & & &\\

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''. 
 \end{itemize}

@@

We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

The {\it A} column in Figure~\ref{templates} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g. 52\% for ``believe that'').

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006} seems to have sparked extra controversy.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}
